Estimating associations between childhood exposure to non-persistent endocrine disruptors, corticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2023-12-19 output/paper/_figures.qmd
Forst plots with multi-outcome for RQ2.

@@

```{r marginal-1}
#| label: fig-marginal-1
#| fig-cap: Average comparisons
#| fig-width: 6
#| fig-height: 7

tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```

```{r marginal-2}
#| label: fig-marginal-2
#| fig-cap: Average comparisons
#| fig-width: 9
#| fig-height: 10

tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```

```{r marginal-3}
#| label: fig-marginal-3
#| fig-cap: Average comparisons
#| fig-width: 5
#| fig-height: 5

tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```

>>>>

```{r}
# Function to align forest plot with table numerical results
forest_plot <- function(obj, r = 4) {
  # From table of numerical results to ggplot object
  tbl_num_res <- obj$numerical_results |>
    tidylog::mutate(
      variable = forcats::fct_reorder2(
        variable, estimate, class
      )
    ) |>
    tidylog::select(-estimate) |>
    ggplot2::ggplot(
      ggplot2::aes(
        y = variable,
        shape = outcome
      )
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 0,
        label = variable
      ),
      hjust = 0,
      fontface = "bold"
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 1,
        label = val
      ),
      hjust = 0,
      position = ggstance::position_dodgev(height = 0.9)
    ) +
    ggplot2::theme_void() +
    ggplot2::theme(
      strip.background = ggplot2::element_blank(),
      strip.text = ggplot2::element_blank(),
      legend.position = "bottom",
      legend.box = "vertical",
      legend.margin = ggplot2::margin()
    ) +
    ggplot2::coord_cartesian(
      xlim = c(0, 4)
    )

  # Assemble elements
  ret <- patchwork::wrap_plots(
    tbl_num_res, obj$plot
  ) +
    patchwork::plot_layout(
      design = c(
        patchwork::area(t = 0, l = 1, b = 3, r = r),
        patchwork::area(t = 1, l = r, b = 3, r = r + 4)
      )
    )

  return(ret)
} # End function forest_plot
```

@@

```{r marginal-1}
#| label: fig-marginal-1
#| fig-cap: Marginal comparison results for $hitrtse \sim edc$
#| fig-width: 9
#| fig-height: 10

obj1 <- tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj1)
```

```{r marginal-2}
#| label: fig-marginal-2
#| fig-cap: Marginal comparison results for $production \sim edc$
#| fig-width: 9
#| fig-height: 12

obj2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = c(
    "cortisol production",
    "cortisone production",
    "corticosterone production"
  ),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj2)
```

```{r marginal-3}
#| label: fig-marginal-3
#| fig-cap: Marginal comparison results for $hitrtse \sim metabolite$
#| fig-width: 9
#| fig-height: 5

obj3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj3, r = 5)
```
